### 2022-09-12 draft.tex
Deploying to gh-pages from @ PoisotLab/manuscript-template@e2d1f3d8de8f52c9d1227cf237fc2a0b94f8ba4a 🚀

This template uses \texttt{pandoc} (and a few additional python glue
scripts) to facilitate the production of scientific articles using a
standard markdown file. The objective is to ensure that standard
markdown (with the important exception of the \texttt{pandoc-crossref}
citation markup) will be rendered into an interactive website (which
allows collaborative annotations with the \texttt{hypothes.is}
platform), a ``draft'' style PDF (double-spaced, numbered lines, figures
at the end), and a ``preprint'' style PDF (with slightly more
reader-friendly pagination).

>>>>

This template uses \texttt{pandoc} (and a few additional \emph{Julia}
glue scripts) to facilitate the production of scientific articles using
a standard markdown file. The objective is to ensure that standard
markdown (with the important exception of the \texttt{pandoc-crossref}
citation markup) will be rendered into an interactive website (which
allows collaborative annotations with the \texttt{hypothes.is}
platform), a ``draft'' style PDF (double-spaced, numbered lines, figures
at the end), and a ``preprint'' style PDF (with more reader-friendly
pagination).
